---
title       : Developing Data Products
subtitle    : Exponential distribution vs Central Limit Theorem
author      : Dinh Huy Hoang, 25 Sep 2015
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [mathjax, quiz, bootstrap]            # {mathjax, quiz, bootstrap}
mode        : standalone # {standalone, draft,selfcontained}
knit        : slidify::knit2slides
---

## Exponential distribution in R and compare it with the Central Limit Theorem (CLT)

<br>
`1) Central Limit Theorem`

  * States that the distribution of averages of iid variables (properly normalized)
  * Becomes that of a standard normal distribution as the sample size n increases large enough

<br>
`2) The exponential distribution` 
  
  * Have mean = 1/lambda 
  * Standard deviation is equal to the mean.

<br>
`3) Investigate how the arithmetic mean of Exponential distribution iid variables converges to a normal distribution.` 


--- .class #id 

## Exponential distribution 

* Use rexp(n, lambda) in R to simulate the exponential distribution 
* Lambda is the rate parameter and set 0.2
* Sampling size is given 40
* Number of simulation is given 1000

```{r}
set.seed(100)       # For reproducible 
lambda <- 0.2; sam <- 40; sim <- 1000       # lambda, sampling size, number of distributions 
means <- NULL       # set msn to null to avoid duplication data 
for (i in 1 : sim) means <- c(means, mean(rexp(sam,lambda))) 
sample_mean <- data.frame(means) 
th_mean <- 1/lambda                               # Theoretical mean
average <- mean(sample_mean$means)                # Simulation mean
th_var  <- ((1/lambda)^2)/sam                     # Theoretical variance 
var_mean<- var(sample_mean$means)                 # variance of the means 
```

--- .class #id
## Exponential distribution (cont 2)

```{r}
print(th_mean); print(average)
```
* The result of mean is quite similar between simulation and Theory 
```{r}
print(th_var); print(var_mean)
```
* The result of variance of mean is close between simulation and Theory 

--- .class #id

## Exponential distribution (cont 3)
* Increase number of simulation to 10000
```{r, echo=FALSE}
set.seed(100)       # For reproducible 
lambda <- 0.2; sam <- 40; sim <- 10000       # lambda, sampling size, number of distributions 
means <- NULL       # set msn to null to avoid duplication data 
for (i in 1 : sim) means <- c(means, mean(rexp(sam,lambda))) 
sample_mean <- data.frame(means) 
th_mean <- 1/lambda                               # Theoretical mean
average <- mean(sample_mean$means)                # Simulation mean
th_var  <- ((1/lambda)^2)/sam                     # Theoretical variance 
var_mean<- var(sample_mean$means)                 # variance of the means 
```

```{r}
print(th_mean); print(average); print(th_var); print(var_mean)
```

* The result of mean and variance of the mean is similar between simulation and Theory 

`Conclusion`: When the number of simulation increase(large enough), there is evolution from Exponential to Normal distribution(Central Limit Theorem) 

